---
# Get YAML keywords from myYAML_ref.Rmd
title: "Motor Trend: mpg regression"
author: "bdanalytics"
#output: html_document
---
#### Date: `r format(Sys.time(), "(%a) %b %d, %Y")`

Data: Device data is from an anonymous individual whose number of steps was sampled in 5 minute intervals.  
Source: 
Time period: October and November, 2012

### Synopsis:

Potential next steps include:

```{r set_global_options}
rm(list=ls())
set.seed(12345)
source("~/Dropbox/datascience/R/mydsutils.R")
source("~/Dropbox/datascience/R/myplot.R")
# Gather all package requirements here
#suppressPackageStartupMessages(require())
```

```{r set_global_options_wd, echo=FALSE}
setwd("~/Documents/Work/Courses/Coursera/jhu-datascience/E-Reproducible-Research/PA1")
```

### Step 01: import data
```{r import_data, cache=TRUE}


```

#### Step 02.1: inspect data
```{r inspect_steps_1, cache=TRUE}
print(str(entity_df))

# List info gathered for various columns
# steps:
# date:
# interval:

print(summary(entity_df))
pairs(subset(entity_df, select=-c(col_symbol)))

# Create new features that help diagnostics
```

Null Hypothesis ($\sf{H_{0}}$): mpg is not impacted by am_fctr.  
The variance by am_fctr appears to be independent. 
```{r q1, cache=TRUE}
print(t.test(subset(cars_df, am_fctr == "automatic")$mpg, 
             subset(cars_df, am_fctr == "manual")$mpg, 
             var.equal=FALSE)$conf)
```
We reject the null hypothesis i.e. we have evidence to conclude that am_fctr impacts mpg (95% confidence). Manual transmission is better for miles per gallon versus automatic transmission.

```{r print_sessionInfo, echo=FALSE}
sessionInfo()
```