---
# Get YAML keywords from myYAML_ref.Rmd
title: "Motor Trend: mpg regression"
author: "bdanalytics"
#output: html_document
---
#### Date: `r format(Sys.time(), "(%a) %b %d, %Y")`

Data: Device data is from an anonymous individual whose number of steps was sampled in 5 minute intervals.  
Source: 
Time period: October and November, 2012

### Synopsis:

Potential next steps include:

```{r set_global_options}
rm(list=ls())
set.seed(12345)
source("~/Dropbox/datascience/R/mydsutils.R")
source("~/Dropbox/datascience/R/myplot.R")
# Gather all package requirements here
#suppressPackageStartupMessages(require())

library(sos)
findFn("cosine", maxPages=2, sortby="MaxScore")
```

```{r set_global_options_wd, echo=FALSE}
setwd("~/Documents/Work/Courses/Coursera/jhu-datascience/E-Reproducible-Research/PA1")
```

### Step 01: import data
```{r import_data, cache=TRUE}


```

#### Step 02.1: inspect data
```{r inspect_steps_1, cache=TRUE}
print(str(entity_df))
#View(entity_df)

# List info gathered for various columns
# steps:
# date:
# interval:

print(summary(entity_df))
pairs(subset(entity_df, select=-c(col_symbol)))

# Create new features that help diagnostics
#   Convert factors to dummy variables
#   Build splines   require(splines); bsBasis <- bs(training$age, df=3)

```

Null Hypothesis ($\sf{H_{0}}$): mpg is not impacted by am_fctr.  
The variance by am_fctr appears to be independent. 
```{r q1, cache=TRUE}
print(t.test(subset(cars_df, am_fctr == "automatic")$mpg, 
             subset(cars_df, am_fctr == "manual")$mpg, 
             var.equal=FALSE)$conf)
```
We reject the null hypothesis i.e. we have evidence to conclude that am_fctr impacts mpg (95% confidence). Manual transmission is better for miles per gallon versus automatic transmission.

## remove nearZeroVar features (not much variance)
#require(reshape)
#var_features_df <- melt(summaryBy(. ~ factor(0), data=entity_df[, features_lst], 
#                             FUN=var, keep.names=TRUE), 
#                             variable_name=c("feature"))
#names(var_features_df)[2] <- "var"
#print(var_features_df[order(var_features_df$var), ])
# summaryBy ignores factors whereas nearZeroVar inspects factors

# k_fold <- 5
# entity_df[order(entity_df$classe, 
#                   entity_df$user_name, 
#                   entity_df$my.rnorm),"my.cv_ix"] <- 
#     rep(1:k_fold, length.out=nrow(entity_df))
# summaryBy(X ~ my.cv_ix, data=entity_df, FUN=length)
# tapply(entity_df$X, list(entity_df$classe, entity_df$user_name, 
#                            entity_df$my.cv_ix), length)

#require(DAAG)
#entity_df$classe.proper <- as.numeric(entity_df$classe == "A")
#rnorm.glm <- glm(classe.proper ~ rnorm, family=binomial, data=entity_df)
#cv.binary(rnorm.glm, nfolds=k_fold, print.details=TRUE)
#result <- cv.lm(df=entity_df, form.lm=formula(classe ~ rnorm), 
#                    m=k_fold, seed=12345, printit=TRUE)

#plot(mdl_1$finalModel, uniform=TRUE, main="base")
#text(mdl_1$finalModel, use.n=TRUE, all=TRUE, cex=0.8)


```{r print_sessionInfo, echo=FALSE}
sessionInfo()
```